Analysis

### 2021-04-25 analysis.Rmd
analysis commit

```{r global_options, echo=FALSE, include = FALSE}
knitr::opts_chunk$set(#
  fig.path="Figs/", 
  message=FALSE, 
  warning=FALSE,
  collapse =TRUE,
  echo=FALSE, 
  #results="hide", 
  fig.width= 10,
  fig.height=10,
  tidy = "styler")
```
```{r runanalysis, echo=FALSE, include = FALSE}
source("libs.R") # libraries 
source("funs.R") # custom functions
```

@@

```{r}
# import data
d <- data_read_mymachine()
```

@@

Next we need to examine patterns of missingness, which might spoil inference.

@@

```{r}
m1 <- brm(
  anx_s ~ ch_s +
    age_s  +
    male +
    (1 + ch_s | country),
  data = d1,
  family = "gaussian",
  seed = 1234,
  warmup = 1000,
  iter = 3000,
  chains = 4,
  file = "m1"
)
parameters::model_parameters(m1, test = "p_direction")
parameters::random_parameters(m1)
```

@@

```{r}
samples1 <- brms::prior_samples(m1, "b_ch_s")
samples1
```

>>>>

```{r global_options, echo=FALSE, include = FALSE}
knitr::opts_chunk$set(#
  fig.path="Figs/", 
  message=FALSE, 
  warning=FALSE,
  collapse =TRUE,
  echo=FALSE, 
  #results="hide", 
  fig.width= 10,
  fig.height=10,
  tidy = "styler")
```
```{r runanalysis, echo=FALSE, include = FALSE}
source("libs.R") # libraries 
source("funs.R") # custom functions

# libraries
# libraries and settings
library("tidyverse")
library("easystats")
library("ggplot2") #plots
library("sjstats") #test statistics
library("sjPlot")
library("sjmisc")
library("insight")
library("see")
library("performance")
library("ggraph")
library("parameters")
library("lme4")
library("psych") ## correlation matrix
library("table1")
library("ggeffects")
library("gghighlight")
#library("naniar") # missingness
#library("Amelia")
#library("magrittr")
library("patchwork")
library("texreg")
library("viridis")
library("ggpubr")
library("ggsci") 
library("here")
library("citr")
library("rethinking")
#library("statsExpressions")
library("ggstatsplot")
library("ggthemes")
library("ggdag")
library("papaja")
library("rstan")
library("brms")
library("tidybayes")
library("bayesplot")
library("dagitty")
library("ggdag")
rstan_options(auto_write=TRUE)
options(mc.cores=parallel::detectCores ())
theme_set(theme_few())
```

@@

```{r}
# import data
d <- as.data.frame(
  read.csv(here::here("MARP_data_blinded.csv")
  )
)
```

@@

Next we need to examine patterns of missing-ness, which might spoil inference.

@@

```{r}
m1 <- brm(
  anx_s ~ ch_s +
    age_s  +
    male +
    (1 + ch_s | country),
  sample_prior = TRUE,
  data = d1,
  family = "gaussian",
  seed = 1234,
  warmup = 1000,
  iter = 3000,
  chains = 4,
  file = "m1"
)
parameters::model_parameters(m1, test = "p_direction")
parameters::random_parameters(m1)
```

@@

```{r}
library(coda)
samples1 <- brms::prior_samples(m1, "b_ch_s")
```
